Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-05 paper.tex
Added NAFNet reference citation

\subsection{Model Architecture}
To evaluate Augraphy, we trained two simple models: the first was a UNet convolutional neural network, taken directly from a submission to the NoisyOffice Kaggle competition  \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}. We selected this one for its simplicity and the clarity of its exposition, and use it with few changes. The second model is an off-the-shelf Nonlinear Activation-Free Network, \cite{NAFNet}; we again made only minor changes to the model's training hyperparameters, increasing the batch size to fit our data.

>>>>

\subsection{Model Architecture}
To evaluate Augraphy, we trained two simple models: the first was a UNet convolutional neural network, taken directly from a submission to the NoisyOffice Kaggle competition  \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}. We selected this one for its simplicity and the clarity of its exposition, and use it with few changes. The second model is an off-the-shelf Nonlinear Activation-Free Network (NAFNet), \cite{ref_nafnet}; we again made only minor changes to the model's training hyperparameters, increasing the batch size to fit our data.
